---
title: "R code integration"
author: "RunWithAI"
date: 2026-09-24
engine: knitr
execute:
  message: false
format: html
---

# Using R in Web Pages

This page was created following the guidelines from [UBC MDS DSCI 521 milestone3](https://ubc-mds.github.io/DSCI_521_platforms-dsci/assignments/milestone3.html) . The dataset is loaded via library palmerpenguins. 

## Dataset

We use the [Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/) dataset to demonstrate how to embed R code and its output into an HTML page via Quarto.

## R code
First, we load the penguin dataset and inspect its contents.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#| message: false
library(tidyverse)
library(palmerpenguins)

head(penguins)
```

Now, let's find the average bill length (mm) of Adelie penguins on Torgersen Island.

```{r}
pgs <- penguins |> filter(species == 'Adelie' & island == 'Torgersen') |>
    select("bill_length_mm") |>
    map_dbl(mean, na.rm = TRUE)

```

The average bill length of Adelie penguins on Torgersen Island is `{r} round(pgs, 1)` mm.


## References

1. [Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/)
2. [UBC MDS DSCI 521 milestone3](https://ubc-mds.github.io/DSCI_521_platforms-dsci/assignments/milestone3.html)