---
title: "Rython and R code integration"
author: "RunWithAI"
date: 2026-09-24
engine: knitr
execute:
  message: false
format: html
---

# Mix R and Python on web page

This page was created following the guidelines from [UBC MDS DSCI 521 milestone3](https://ubc-mds.github.io/DSCI_521_platforms-dsci/assignments/milestone3.html) . 

## Dataset

We use the [Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/) dataset which is loaded via R library palmerpenguins and used by R and Python together.

## Load penguins with R code

First step, we use R to load the pengiuin data set and check what it has. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#| message: false

library(reticulate)
# py_config()
library(tidyverse)
library(palmerpenguins)
head(penguins)
```

## Access R Object using Python code

Then we use Python to use the penguins object from R context and calculate the average bill length (mm) of Adelie pengiuns on Torgersen island. 

```{python}
from IPython.display import display
# use penguins from R context
penguins = r.penguins
display(penguins.describe())
print("\n")
display(penguins.head())

pats = penguins.query("species == 'Adelie' and island == 'Torgersen'" )
bill_length_mean = pats['bill_length_mm'].mean()
bill_length_mean
```


## Access Python object using R code

Then we use R to access the object of 'bill_length_mean' defined in Python context and output its value.

```r
round(py$bill_length_mean, 1)
```

The average bill length of Adelie pengiuns on Torgersen is `{r} round(py$bill_length_mean, 1)` mm.


## Using R code to draw a figure


```{r}
#| label: fig-bill-length-species
#| fig-cap: "Distribution of bill length across penguin species."
#| message: false
#| warning: false
#| 
penguins |>
  drop_na(bill_length_mm) |>
  ggplot(aes(x = species, y = bill_length_mm, fill = species)) +
  geom_boxplot(alpha = 0.6, width = 0.5, outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.4, size = 1.8) +
  stat_summary(fun = mean, geom = "point", shape = 18, size = 3.5, color = "darkred") +
  labs(
    x = "Species",
    y = "Bill Length (mm)",
    title = "Bill Length Distribution by Species",
    subtitle = "Diamonds indicate the mean bill length for each species"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

## References

1. [Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/)
2. [UBC MDS DSCI 521 milestone3](https://ubc-mds.github.io/DSCI_521_platforms-dsci/assignments/milestone3.html)