---
title: "Rython and R code integration"
author: "RunWithAI"
date: 2026-09-22
engine: knitr
execute:
  message: false
format: html
---

# Mix R and Python on web page

This page was created following the guidelines from [UBC MDS DSCI 521 milestone3](https://ubc-mds.github.io/DSCI_521_platforms-dsci/assignments/milestone3.html) . The dataset is loaded via R library palmerpenguins. 

## R code

First step, we use R to load the pengiuin data set and check what it has. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#| message: false

library(reticulate)
py_config()
library(tidyverse)
library(palmerpenguins)

head(penguins)
```

## Python code

Then we use Python to use the penguins object from R context and calculate the average bill length (mm) of Adelie pengiuns on Torgersen island. 

```{python}
from IPython.display import display
# use penguins from R context
penguins = r.penguins
display(penguins.describe())
print("\n")
display(penguins.head())

pats = penguins.query("species == 'Adelie' and island == 'Torgersen'" )
bill_length_mean = pats['bill_length_mm'].mean()
bill_length_mean
```


## R code

Then we use R to access the object of 'bill_length_mean' defined in Python context and output its value.

```r
round(py$bill_length_mean, 1)
```

The average bill length of Adelie pengiuns on Torgersen is `{r} round(py$bill_length_mean, 1)` mm.


## References

1. [Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/)
2. [UBC MDS DSCI 521 milestone3](https://ubc-mds.github.io/DSCI_521_platforms-dsci/assignments/milestone3.html)